Inference using context-dependent models of mutation

### 2017-05-10 writeups/context-dependence.tex
updated ising results in writeup

\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
    & (4,1,1) & (5,1,1) & (6,2,2) \\ 
  \hline
  $\lambda_-$ & 0.61 & 0.63 & 0.96 \\ 
  $\lambda_+$ & 0.87 & 0.86 & 0.85 \\ 
  $\beta$     & 0.76 & 0.81 & 0.94 \\ 
  $\gamma$    & 0.69 & 0.76 & 0.85 \\ 
   \hline
\end{tabular}
    \caption{
        Posterior coverage of the four parameters of the dynamic Ising model at four different T-mer sizes.
        Shown are the proportion of runs in which the true value fell within the 95\% credible interval,
        for T-mers of length 4, 5, and 6 with overhangs of length 1, 1, and 2 respectively.
        The total number of runs was 54 for $(6,2,2)$ T-mers and 114 for the others.
        \label{tab:ising_coverage}
    }
\end{table}

\begin{figure}
    \begin{center} 
        \includegraphics{writeup-plots/coverage_results}
    \end{center} 
    \caption{
        Credible intervals for the four parameters of the dynamic Ising model,
        calculated using $(6,2,2)$ T-mers,
        from 54 MCMC runs on independently simulated sequences of $10^6$ bases
        differing at around 18.6\% of the sites.
        Shown are relative intervals, obtained by dividing by the true value.
        \label{fig:ising_coverage}}
\end{figure}

@@

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
    & (4,1,1) & (5,1,1) & (6,2,2) \\ 
  \hline
  $\lambda_-$ & 0.61 & 0.63 & 0.96 \\ 
  $\lambda_+$ & 0.87 & 0.86 & 0.85 \\ 
  $\beta$     & 0.76 & 0.81 & 0.94 \\ 
  $\gamma$    & 0.69 & 0.76 & 0.85 \\ 
   \hline
\end{tabular}
    \caption{
        Posterior coverage of the four parameters of the dynamic Ising model at four different T-mer sizes.
        Shown are the proportion of runs in which the true value fell within the 95\% credible interval,
        for T-mers of length 4, 5, and 6 with overhangs of length 1, 1, and 2 respectively.
        The total number of runs was 61 for $(6,2,2)$ T-mers and 121 for the others.
        \label{tab:ising_coverage}
    }
\end{table}

\begin{figure}
    \begin{center} 
        \includegraphics{writeup-plots/coverage_results}
    \end{center} 
    \caption{
        Credible intervals for the four parameters of the dynamic Ising model,
        calculated using $(6,2,2)$ T-mers,
        from 61 MCMC runs on independently simulated sequences of $10^6$ bases
        differing at around 18.6\% of the sites.
        Shown are relative intervals, obtained by dividing by the true value.
        \label{fig:ising_coverage}}
\end{figure}

@@

\section{Supplementary figures}

\begin{figure}
    \begin{center} 
        \includegraphics{writeup-plots/coverage_results_all}
    \end{center} 
    \caption{
        As in \ref{fig:ising_coverage}:
        Credible intervals for the four parameters of the dynamic Ising model,
        from MCMC runs on independently simulated sequences of $10^6$ bases
        differing at around 18.6\% of the sites.
        Shown are relative intervals, obtained by dividing by the true value.
        The three groups are left to right, credible intervals obtained from $(4,2,1)$, $(5,3,1)$, and $(6,2,2)$ T-mers:
        note that only the longest $(6,2,2)$ T-mers provide well-calibrated coverage (Table \ref{tab:ising_coverage})
        and do not show bias.
        \label{fig:all_ising_coverage}}
\end{figure}
